FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-11 NewVersion/sections/Discussion.tex
Added refs.

\section{Discussion}\label{sec:discussion}
In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
our language to traits, Java interfaces as well as other languages. Furthermore we discuss
ways to improve our  work.\bruno{references please!!!}

@@

Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
to include only method declarations, and those abstract methods can be implemented in a class body. 
The formal Featherweight Java model does not include abstract methods because of its orthogonality to the core calculus. In traits the
similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations. Abstract methods provide a way to
delay the implementations to future subtypes. Using overriding, they also help to ``exclude'' existing implementations.

@@

One typical non-orthogonal extension to our model could be to have fields. Having fields in OO multiple inheritance is a non-trivial issue. There has been a lot of work on it, such as C++ that uses virtual inheritance. The trait model simply disallows state to avoid that issue. In our language, however, we can perhaps borrow the idea of \textit{interface-based programming} [], which actually models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. To directly support fields it requires more discussions and experiments, we leave them as our future work.

>>>>

\section{Discussion}\label{sec:discussion}
In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
our language to traits, Java interfaces as well as other languages. Furthermore we discuss
ways to improve our  work.\bruno{references please!!!} \haoyuan{Done}

@@

Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
to include only method declarations, and those abstract methods can be implemented in a class body. 
The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of its orthogonality
to the core calculus. In traits the
similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations~\cite{scharli03traits}.
Abstract methods provide a way to
delay the implementations to future subtypes. Using overriding, they also help to ``exclude'' existing implementations.

@@

One typical non-orthogonal extension to our model could be to have fields. Having fields in OO multiple inheritance is a non-trivial issue. There has been a lot of work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}. The trait model simply disallows state to avoid that issue. In our language, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which actually models state with abstract state operations. This can be realized by extending our current model with static methods and anonymous classes from Java. To directly support fields it requires more discussions and experiments, we leave them as our future work.
